---
title: "Hypothermia Electrolyte Protocol - Regression Models"
author: "Michael Ha, Jennifer Gass"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r data, echo=FALSE, message=FALSE}
library(readxl)
library(dplyr)
library(broom)
library(pander)

data <- read_excel("data/data.xlsx")
names(data) <- make.names(names(data))

data <- data %>%
    mutate(RRT.prior.to.arrest = ifelse(RRT.prior.to.arrest == "Y", TRUE, FALSE),
           Initial.rhythm = factor(Initial.rhythm),
           APACHE.II = ifelse(APACHE.II <= 15, "A", 
                              ifelse(APACHE.II >= 16 & APACHE.II <= 20, "B",
                                     ifelse(APACHE.II >= 21 & APACHE.II <= 25, "C",
                                            ifelse(APACHE.II >= 26 & APACHE.II <= 30, "D", "E")))),
           APACHE.II = factor(APACHE.II),
           SOFA = ifelse(SOFA <= 6, "A",
                         ifelse(SOFA >= 7 & SOFA <= 9, "B",
                                ifelse(SOFA >= 10 & SOFA <= 12, "C",
                                       ifelse(SOFA >= 13 & SOFA <=14, "D", "E")))),
           SOFA = factor(SOFA),
           RIFLE = factor(RIFLE)) %>%
    filter(!is.na(Patient)) %>%
    rename(Age = Age..Years..Visit.)

```

## Initial Potassium

### Linear Regression Model

```{r}
regr <- select(data, Age, Initial.rhythm:First.Potassium)
mod1 <- lm(First.Potassium ~ ., data = regr, na.action = na.exclude)
```

#### Model Statistics
```{r echo=FALSE}
pander(glance(mod1))
```

#### Coefficients
```{r echo=FALSE}
pander(tidy(mod1))
```

### Backwards Stepwise Regression

```{r}
mod2 <- step(mod1, trace = 0)
# , k = log(nrow(regr))
```

#### Model Statistics
```{r echo=FALSE}
pander(glance(mod2))
```

#### Coefficients
```{r echo=FALSE}
pander(tidy(mod2))
```

#### Residuals Plot

```{r}
par(mfrow=c(2,2))
plot(mod2)
```

## Rewarmed Potassium Below Goal >= 50% of Time

```{r}
regr <- select(data, Age, Initial.rhythm:SCr.on.admission, Rewarmed.Potassium...below) %>%
    mutate(Rewarmed.Potassium.Low = ifelse(Rewarmed.Potassium...below >= 0.5, TRUE, FALSE)) %>%
    select(-Rewarmed.Potassium...below)

mod1 <- glm(Rewarmed.Potassium.Low ~ ., data = regr, family = binomial, na.action = na.exclude)
```

#### Model Statistics
```{r echo=FALSE}
pander(glance(mod1))
```

#### Coefficients
```{r echo=FALSE}
pander(tidy(mod1))
```

### Backwards Stepwise Regression

```{r}
mod2 <- step(mod1, trace = 0)
# , k = log(nrow(regr))
```

#### Model Statistics
```{r echo=FALSE}
pander(glance(mod2))
```

#### Coefficients
```{r echo=FALSE}
pander(tidy(mod2))
```

#### Residuals Plot

```{r}
par(mfrow=c(2,2))
plot(mod2)
```

### References

Data was processed using `r R.Version()$version.string` on a `r R.Version()$platform` system.

Prepared by: Brian Gulbis

```{r echo=FALSE}
citation()
```

